04_DESeq_sexes

### 2019-08-28 analysis/04_DESeq2_sexes.Rmd
less text

  # LDA analysis
  # Fit the model
  print(model <- lda(treatment~ sex, data = train.transformed))
  # Make predictions
  print(predictions <- model %>% predict(test.transformed))
# Model accuracy
  print(mean(predictions$class==test.transformed$treatment))

>>>>

  # LDA analysis
  # Fit the model
  model <- lda(treatment~ sex, data = train.transformed)
  # Make predictions
  predictions <- model %>% predict(test.transformed)
  # Model accuracy
  mean(predictions$class==test.transformed$treatment)
